\cvsection{Experiences}

\cvevent{DevOps Engineer \& Full-Stack Developer – Freelance}{Cesar Richard EI}{June 2022 -- Present}{Compiègne \faGlobe (Full Remote)}
\begin{itemize}
    \item \textbf{Pasqal (since Oct. 2022)} — Automated system and software deployments \textit{(Ansible, Terraform)}; designed and optimized CI/CD pipelines \textit{(GitLab CI)}; built internal tools to enhance developer experience (DX); monitored physical machines and Kubernetes clusters \textit{(Prometheus)}.
    \item \textbf{Pumpkin (since Oct. 2023)} — Designed and developed a custom web platform for emergency services management: operational planning, equipment assignment, inventory compliance and expiration tracking. \textit{(Django, ReactJS, Kubernetes, CI/CD)}
    \item \textbf{Identibat (June – Sept. 2022)} — Defined software and infrastructure architecture, implemented CI/CD pipelines and Kubernetes deployments. \textit{(Terraform, Django, ReactJS)}
\end{itemize}

\divider

\cvevent{Cashless, Ticketing \& Access Control Expert (Freelance)}{Weezevent}{Jan 2019 -- Present}{On-site assignments}
\begin{itemize}
    \item Technical support and on-site expertise for ticketing, contactless payment and access control systems at festivals, trade shows, and concerts. Preparation, deployment and live operations with client and technical teams.
\end{itemize}

\divider

\cvevent{Full-Stack Developer}{Weezevent (Permanent contract)}{Jan 2019 -- Dec 2021}{Saint-Denis}
\begin{itemize}
    \item Developed and maintained the company’s ticketing, cashless and payment solutions based on a microservices architecture. \textit{(PHP, Symfony, Python, Django, ReactJS)}
    \item Provided technical support for key accounts and on-site assistance during major events.
    \item Infrastructure as Code deployments. \textit{(Terraform)}
\end{itemize}

\divider

\cvevent{Head of Scientific Computing Service (IT Department)}{Université Paris-Saclay}{Apr 2017 -- Jan 2019}{Orsay}
\begin{itemize}
    \item Managed the Scientific Computing Division of the central IT department: project coordination, license management, technical support, and campus-wide IT initiatives.
    \item Supported research projects involving big data and cloud computing technologies: \textit{(Hadoop, Spark, OpenShift, system administration, Java, Matlab)}
\end{itemize}

\divider

\cvevent{Research Engineer}{French National Centre for Scientific Research (CNRS)}{Sept 2012 -- Apr 2017}{Compiègne}
\begin{itemize}
    \item Designed and developed a 3D simulation framework for autonomous drones \textit{(C++, Qt)}.
    \item Installed and calibrated a motion capture system \textit{(network, sensors, optics)}.
    \item Provided technical and scientific support for various research projects in collaboration with industrial partners, including a major automotive manufacturer.
    \item Worked on embedded development, scientific data management, and project coordination.
    \item Built a data promotion platform to valorize the datasets produced by the lab \textit{(system administration, PHP, Symfony, C++)}.
\end{itemize}
